---
title: "Prediction"
author: "Xiaoyang Li"
date: "2020/11/5"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(MASS)
library(caret)
library(rpart)
library(rpart.plot)
```

## Data clean
```{r}

# data import
data = read_delim("data.dat", "\t", escape_double = FALSE, trim_ws = TRUE) 

# 96 patients and remove comments column
data = data[1:96,] %>% dplyr::select(SurgPathFindings,SeqentialStaging, Largestdiameterofappendixmeasuredanteriortoposteriorwithcompre_A, Maximalmuralthicknessdistancefromhyperechoicluminalinterfaceto_A,  Presenceoffecalith_A, Presenceofsurroundingfreefluid_A) %>% 
  rename(Surg = SurgPathFindings,
         US2 = SeqentialStaging,
         Appdiam = Largestdiameterofappendixmeasuredanteriortoposteriorwithcompre_A,
         Muralthick = Maximalmuralthicknessdistancefromhyperechoicluminalinterfaceto_A,
         fecalith = Presenceoffecalith_A,
         freefluid = Presenceofsurroundingfreefluid_A) %>% 
  mutate(surg_bi = case_when(Surg >=3 ~ 1,
                             Surg <3 ~ 0),
         US2_ = case_when(US2 >=3 ~ 1,
                         US2 <3 ~ 0),
         lossSM = case_when(US2 == 4 ~ "1",
                            US2 != 4 ~ "0"),
         Muralthick = as.numeric(Muralthick),
         freefluid = case_when(freefluid == "Yes" ~"Yes;",
                               freefluid != "Yes" ~ freefluid)
         ) 
US = data %>% dplyr::select(US2_, surg_bi)
US = drop_na(US)

data$fecalith[data$fecalith == "Missing"] = NA
data$freefluid[data$freefluid == "Missing"] = NA

data = data %>% dplyr::select(surg_bi, Appdiam, Muralthick, fecalith , freefluid , lossSM)
data = drop_na(data) # 61
str(data) 
```

1) loss of normal echogenic submucosal layer: In the dataset, loss of SM layer is captured by the ultrasound and is described as stage IV: Gangrenous.
2) mural hyperemia: Maximum mural thickness 
3) periappendiceal fluid: Presence of surrounding free fluid
4) appendicolith: presence of fecalith
5) appendix wall diameter: largest diameter of appendix


## Logistic regression
```{r}
# choose model
glm1 = glm(data = data, surg_bi ~ . , family=binomial(link='logit')) 
summary(glm1)

step = glm2 %>% stepAIC(trace = FALSE)
glm2 = glm(data = data, surg_bi ~ Appdiam + fecalith + freefluid , family=binomial(link='logit')) 
summary(glm2)

data_ = data %>% mutate(
  freefluidcom = case_when(freefluid == "Yes; complex" ~ "1",
                           freefluid != "Yes; complex" ~ "0"),
  freefluid_ = case_when(freefluid == "Yes; complex" ~ "1",
                         freefluid == "Yes; simple" ~ "1",
                         freefluid == "Yes;" ~ "1",
                         freefluid == "No" ~ "0")
)

glm3 = glm(data = data_,surg_bi ~ Appdiam + Muralthick +  fecalith + freefluid_ + lossSM , family=binomial(link='logit')) 
summary(glm3)
step3 = glm3 %>% stepAIC(trace = FALSE)
glm3_ = glm(formula = surg_bi ~ Appdiam + fecalith, family = binomial(link = "logit"), 
    data = data_)
summary(glm3_)



glm4 = glm(data = data_, surg_bi ~ Appdiam + Muralthick +  fecalith + freefluidcom + lossSM, family=binomial(link='logit')) 
summary(glm4)
step4 = glm4 %>% stepAIC(trace = FALSE)
glm4_ = glm(formula = surg_bi ~ Appdiam + fecalith + freefluidcom, family = binomial(link = "logit"), 
    data = data_)
summary(glm4_)


# prediction

glm = glm3_
glm_prob = predict(glm, newdata = data_, type = "response")
glm_pred = rep("0", 61)
glm_pred[glm_prob >0.5] = "1"
confusionMatrix(data = as.factor(glm_pred),
                   reference = as.factor(data_$surg_bi), positive = "1")

glm = glm4_
glm_prob = predict(glm, newdata = data_, type = "response")
glm_pred = rep("0", 61)
glm_pred[glm_prob >0.5] = "1"
confusionMatrix(data = as.factor(glm_pred),
                   reference = as.factor(data_$surg_bi), positive = "1")


confusionMatrix(data = as.factor(US$US2_),
                   reference = as.factor(US$surg_bi), positive = "1")
```

## Decision tree
```{r}
rpart1 = rpart(surg_bi ~ Appdiam + Muralthick +  fecalith + freefluid_ + lossSM,
   method="class", data=data_)
rpart2 = rpart(surg_bi ~ Appdiam + Muralthick +  fecalith + freefluidcom + lossSM,
   method="class", data=data_)

print(rpart1)
print(rpart2)
rpart.plot(rpart1)
rpart.plot(rpart2)

```


