---
title: "Summary table"
author: "Xiaoyang Li"
date: "2020/10/8"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = F,message = F)
library(tidyverse)
library(chron)
library(qwraps2)
options(qwraps2_markup = "markdown")
```



```{r}
# Data import
data = read_csv("C:/Users/Xiaoyang Li/Desktop/data/App/appUS1.csv") %>% 
  mutate(PatientHeightandWeightHeightin =  ifelse(PatientHeightandWeightHeightin == 0 ,
                                   NA,
                                   PatientHeightandWeightHeightin))



# Summary
sum = list(
  "Age" = 
    list(
      "mean (sd)" = ~  mean_sd(data$PatientAge),
      "Range" = ~ paste(min(data$PatientAge),max(data$PatientAge), sep = "-")),
  "Gender" = 
    list(
      "Female" = ~ qwraps2::n_perc(data$Gender == "Female"),
      "Male" = ~ qwraps2::n_perc(data$Gender == "Male")),
  "Height(Inch)" = 
    list(
      "mean (sd)" = ~  mean_sd(data$PatientHeightandWeightHeightin[!is.na(data$PatientHeightandWeightHeightin)]),
      "Range" = ~ paste(min(data$PatientHeightandWeightHeightin[!is.na(data$PatientHeightandWeightHeightin)]),max(data$PatientHeightandWeightHeightin[!is.na(data$PatientHeightandWeightHeightin)]) , sep = "-"),
      "NA(%)" = ~paste0(round(sum(is.na(data$PatientHeightandWeightHeightin)) / 96 *100,3), "%")),
  "Weight(Kg)" = 
    list(
      "mean (sd)" = ~  mean_sd((data$PatientHeightandWeightWeightkg[!is.na(data$PatientHeightandWeightWeightkg)])),
      "Range" = ~ paste(min(data$PatientHeightandWeightWeightkg[!is.na(data$PatientHeightandWeightWeightkg)]),max(data$PatientHeightandWeightWeightkg[!is.na(data$PatientHeightandWeightWeightkg)]), sep = "-"),
      "NA(%)" = ~paste0(round(sum(is.na(data$PatientHeightandWeightWeightkg)) / 96 *100,3), "%")),
  "Department 1st" = 
    list(
      "POCUS" = ~ qwraps2::n_perc(data$Whichdepartmentperformedtheultrasoundforthisform[!is.na(data$Whichdepartmentperformedtheultrasoundforthisform)] == "POCUS"),
      "RADUS" = ~ qwraps2::n_perc(data$Whichdepartmentperformedtheultrasoundforthisform[!is.na(data$Whichdepartmentperformedtheultrasoundforthisform)] == "RADUS"),
      "NA(%)" = ~paste0(round(sum(is.na(data$Whichdepartmentperformedtheultrasoundforthisform)) / 96 *100,3), "%")),
  "Department 2nd" = 
    list(
      "POCUS" = ~ qwraps2::n_perc(data$Whichdepartmentperformedtheultrasoundforthisform_A[!is.na(data$Whichdepartmentperformedtheultrasoundforthisform_A)] == "POCUS"),
      "RADUS" = ~ qwraps2::n_perc(data$Whichdepartmentperformedtheultrasoundforthisform_A[!is.na(data$Whichdepartmentperformedtheultrasoundforthisform_A)] == "RADUS"),
      "NA(%)" = ~paste0(round(sum(is.na(data$Whichdepartmentperformedtheultrasoundforthisform_A)) / 96 *100,3), "%")
    ))

summary_table(data, sum)


site =   list(
  "Site" = 
    list(
     "CHLA"   = ~ qwraps2::n_perc(data$SiteName == "CHLA"),
     "CUMC"   = ~ qwraps2::n_perc(data$SiteName == "CUMC"),
     "Denver"   = ~ qwraps2::n_perc(data$SiteName == "Denver"),  
     "Hasbro"  = ~ qwraps2::n_perc(data$SiteName == "Hasbro"),
     "Indiana U"  = ~ qwraps2::n_perc(data$SiteName == "Indiana U"),
     "Minnesota"   = ~ qwraps2::n_perc(data$SiteName == "Minnesota"),   
     "NBIMC"  = ~ qwraps2::n_perc(data$SiteName == "NBIMC"),
     "Rady"   = ~ qwraps2::n_perc(data$SiteName == "Rady"),
     "UC Davis" = ~ qwraps2::n_perc(data$SiteName == "UC Davis")))

summary_table(data, site)

```




|                       |data (N = 96)        |
|:----------------------|:--------------------|
|**Age**                |&nbsp;&nbsp;         |
|&nbsp;&nbsp; mean (sd) |10.99 &plusmn; 4.04  |
|&nbsp;&nbsp; Range     |1.6-18               |
|**Gender**             |&nbsp;&nbsp;         |
|&nbsp;&nbsp; Female    |31 (32.29%)          |
|&nbsp;&nbsp; Male      |65 (67.71%)          |
|**Height(Inch)**       |&nbsp;&nbsp;         |
|&nbsp;&nbsp; mean (sd) |63.02 &plusmn; 23.28 |
|&nbsp;&nbsp; Range     |32-175               |
|&nbsp;&nbsp; NA(%)     |25%                  |
|**Weight(Kg)**         |&nbsp;&nbsp;         |
|&nbsp;&nbsp; mean (sd) |48.69 &plusmn; 24.95 |
|&nbsp;&nbsp; Range     |12-152.3             |
|&nbsp;&nbsp; NA(%)     |1.042%               |
|**Department 1st**     |&nbsp;&nbsp;         |
|&nbsp;&nbsp; POCUS     |28 (30.11%)          |
|&nbsp;&nbsp; RADUS     |64 (68.82%)          |
|&nbsp;&nbsp; NA(%)     |3.125%               |
|**Department 2nd**     |&nbsp;&nbsp;         |
|&nbsp;&nbsp; POCUS     |80 (89.89%)          |
|&nbsp;&nbsp; RADUS     |8 (8.99%)            |
|&nbsp;&nbsp; NA(%)     |7.292%               |


|                       |data (N = 96) |
|:----------------------|:-------------|
|**Site**               |&nbsp;&nbsp;  |
|&nbsp;&nbsp; CHLA      |12 (12.50%)   |
|&nbsp;&nbsp; CUMC      |23 (23.96%)   |
|&nbsp;&nbsp; Denver    |2 (2.08%)     |
|&nbsp;&nbsp; Hasbro    |8 (8.33%)     |
|&nbsp;&nbsp; Indiana U |10 (10.42%)   |
|&nbsp;&nbsp; Minnesota |6 (6.25%)     |
|&nbsp;&nbsp; NBIMC     |14 (14.58%)   |
|&nbsp;&nbsp; Rady      |5 (5.21%)     |
|&nbsp;&nbsp; UC Davis  |16 (16.67%)   |
